Big Data with High Performance Computing (HPC)

### 2016-01-18 Tex_Files/paper.tex
Dadiannao: added block digram of a node
Dadiannao: added block digram of a node and explained why eDRAM over
SRAM.

As we mentioned in the earlier part of this section, memory is thought to be the bottleneck of DianNao.

>>>>

As we mentioned in the earlier part of this section, memory is thought to be the bottleneck of DianNao in convolutional layers with private kernel and classifier layers. The design of Dadiannao as a supercomputer aims to address these problems. First, in order to minimize data movement cost, synapses are placed near to the neurons consuming their data in a fully distributed architecture with no main memory unit. Secondly, nodes are biased towards storing data rather than computation. Thirdly, since the number of synaptic connections is orders of magnitude bigger than neurons,  instead of sending synaptic weights to neurons, neuron values is sent to synapses. This saves a lot in inter node communication bandwidth. Fourthly, intra-node, the storage units are broken into many storage units to increase the bandwidth.\\

The high level architecture of Dadiannao consist of many nodes arranged in a mesh configuration. Each node contains the storage units to store the synaptic and neuron values. In addition a, NFU unit is embedded similar to what introduced in DianNao \cite{chen2014diannao}.The NFU in Dadiannao is capable of carrying out more complex types of computation depending on the layers and mode of operation (training or inferencing). Figure \ref{fig:NFU_Diagram} shows the block diagram of a node for Dadiannao architecture. \\

\begin{figure}[h]
	\includegraphics[scale=0.42]{./images/NFU_diagram.png}
	\centering
	\caption{Block diagram of a node within Dadiannao architecture \cite{chen2014dadiannao}.}
	\label{fig:NFU_Diagram}
\end{figure}
It should be noted that although SRAMs are generally preferred over other types of memory such as DRAM and eDRAM due to the higher speed, their size is limiting factor for them. A typical eDRAM can accommodate more than $2.5\times$ data compared to a SRAM. It should be noted that more storage density is required if parameters of big models are to be stored within chip to avoid external memory access. As a result, eDRAM is selected over SRAM in Dadiannao's proposed design. Refuting the memory bandwidth limitations for for computational units allows for scaling since more inputs and outputs to each neuron can be calculated simultaneously. However, eDRAMs suffer from some drawbacks compared to SRAMs namely, slower response, periodical refreshing requirement, and destructive read that may result in inaccurate values.
